Evaluating computational methods for modeling off-normal operation of gas centrifuge cascades

### 2020-11-05 theory.tex
Adding machines needed per stage information

Here the gas constants are molar mass, $M$, temperature $T$, universal gas constant, $R$,
and the pressure ratio, $x$ (typically $1000:1$).
This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
Otherwise, the relationship can be approximated $\{\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380 \frac{\mathrm{m}}{\mathrm{s}}\}$.
In order to decompose the ratio into each individual radius, knowledge on one
of them is required. Glaser \cite{glaser.2008} states that $r_2$ typically ranges
from 96% to 99% the value of the inner centrifuge wall radius $a$. The exact
behavior of $r_2$ between these two values in operational conditions is unknown,
but a linear approximation can be made. It is assumed that $r_2$ is always at
the midpoint of these two extremes (i.e. $r_2 = 0.975 a$). Then, $r_1$ can be
found by simply multiplying this value by the ratio.

@@

Then, from mass conservation, $N = \theta N' + (1-\theta)N''$, equation
\eqref{eq_product_assay}, and the definition of the abundance, $R$, it is
possible to express $\beta$ as a function of only the feed abundance,
$R$, the cut $\theta$ and $\alpha$:

@@

To construct an ideal cascade stage, a stage cut ($\theta$) must first be computed.
This is found iteratively, searching for the optimal cut value where $\alpha = \beta$
for a given feed and centrifuge parameters. With a separative power calculated,
and $\alpha$ and $\beta$ value can be determined for an initial cut guess. This
model assumes that the ideal cut for a stage should be between 0.1 and 0.9. The
two enrichment factors are compared, and the higher or lower cut value is chosen
by which pair of factors are closer. A new cut is determined from the chosen
factors, a new separative power is computed, and new $\alpha$ and $\beta$ values
are compared. This process continues until, to some precision, the resulting
enrichment factors are approximately equal. As illustrated in Fig. \ref{fig_a_m_b},
for a given input feed assay, the ideal feeding stage typically has a $\theta$
value between 0.45 and 0.525 when $\alpha = \beta$.

@@

From equation \eqref{eq_alpha} and \eqref{eq_beta} it is possible to determine
the cut, $\theta$ required to build an ideal cascade:

As $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of the cut,
$\theta_{i}$, changes across the different stages of a cascade.  This algorithm
assumes that the corresponding separative power $\delta U$ (not re-computed) can
be achieved with the chosen centrifuge design, tuning other operational
parameter such as the rotation speed, the counter-current flow ratio, etc.  Once
$\theta_{i}$ is determined, it is possible to compute the product and the tail
assay.

>>>>

Here the gas constants are molar mass, $M$, temperature $T$, universal gas constant, $R$,
and the pressure ratio, $x$ (typically $1000:1$).
This relationship is valid when $v_a > 380 \frac{\mathrm{m}}{\mathrm{s}}$.
Otherwise, the relationship can be approximated $\{\frac{r_1}{r_2} \approx 0.534 \mid v_a \leq 380 \frac{\mathrm{m}}{\mathrm{s}}\}$.
In order to decompose the ratio into each individual radius, knowledge on one
of them is required. Glaser \cite{glaser.2008} states that $r_2$ typically ranges
from $96\%$ to $99\%$ the value of the inner centrifuge wall radius $a$. The exact
behavior of $r_2$ between these two values in operational conditions is unknown,
but a linear approximation can be made. It is assumed that $r_2$ is always at
the midpoint of these two extremes (i.e. $r_2 = 0.975 a$). Then, $r_1$ can be
found by simply multiplying this value by the ratio.

@@

Then, from mass conservation, $N = \theta N' + (1-\theta)N''$ and equation
\eqref{eq_product_assay}, it is possible to express $\beta$ as a function of
only the feed abundance, $R$, the cut $\theta$ and $\alpha$:

@@

Finally from equation \eqref{eq_alpha} and \eqref{eq_beta} it is possible to
determine the cut, $\theta$ required to build an ideal cascade:

To construct an ideal stage, a cut ($\theta$) must first be computed.
This is found iteratively, searching for the optimal cut value where $\alpha = \beta$
for a given feed and centrifuge parameters. With a separative power calculated,
and $\alpha$ and $\beta$ value can be determined for an initial cut guess. This
model assumes that the ideal cut for a stage should be between 0.1 and 0.9. The
two enrichment factors are compared, and the higher or lower cut value is chosen
by which pair of factors are closer. A new cut is determined from the chosen
factors, a new separative power is computed, and new $\alpha$ and $\beta$ values
are compared. This process continues until, to some precision, the resulting
enrichment factors are approximately equal. As illustrated in Fig. \ref{fig_a_m_b},
for a given input feed assay, the ideal feeding stage typically has a $\theta$
value between 0.45 and 0.525 when $\alpha = \beta$.

@@

The number of machines required to construct a stage can then be computed using
equation \eqref{eq_alpha_principle} to solve for the centrifuge feed flow:

\begin{equation}\label{eq_cent_feed}
    F_c = \frac{2 \delta U}{(\alpha - 1)^2} \frac{M}{M_{238}} \frac{1-\theta}{\theta}
\end{equation}

Where the molar mass ratio $\frac{M}{M_{238}}$ accounts for the molar mass
differences between the feed gas, $UF_6$, and the individual uranium isotopes
being separated. The stage feed flow can then be divided by the individual
centrifuge feed flow, equation \eqref{eq_cent_feed}, to find the exact number of
machines needed for the ideal stage. In practice, this number is rounded up to
account for fractional machines required.

In a cascade, as $\alpha_{i}$ and $\beta_{i}$ remain constant, only the value of
the cut, $\theta_{i}$, changes across the different stages of a cascade.  This
algorithm assumes that the corresponding separative power $\delta U$ (not
re-computed) can be achieved with the chosen centrifuge design, tuning other
operational parameter such as the rotation speed, the counter-current flow
ratio, etc.  Once $\theta_{i}$ is determined, it is possible to compute the
product and the tail assay.
